\problemname{Quality of the Alphabet}

Little Armen and Vartan are studying strings and their properties.
Once they create a string $S$, they write it on a long piece of paper from left to right and cut it in two parts.
Armen takes the left part, Vartan takes the right part.
The parts may contain all the string or none of it.

Armen and Vartan are afraid of string $X_A$ and $X_V$, respectively.
In particular, Armen does not want to get a piece of string, in which $X_A$ appears more than $k_A$ times as a contiguous substring.
Otherwise he is afraid of his piece.
Similarly, Vartan does not want to get a piece of string, where $X_V$ appears more than $k_V$ times as a contiguous substring.

For a string $S$, Armen and Vartan define its quality as the number of ways they can split $S$ into two pieces such that none of them is afraid from their piece.
Then, they quality of the English alphabet is the sum of the qualities of all strings of length $n$ that are composed of lowercase English letters.
Help them find the quality of the English alphabet.

\section*{Input}
The first line of the input contains a single integer $n$ ($1 \leq n \leq 10^9$), the length of the strings.
The second line contains a string and an integer, $X_A$ and $k_A$, respectively, that are space-separated.
The third line contains $X_V$ and $k_V$, in the same format.
It is guaranteed that for $P \in \{ A, V \}$, the string $X_P$ is composed of lowercase English letters, and that $1 \leq k_P \cdot len(X_P) \leq 40$.

\section*{Output}
The only line of the output contains the quality of the English alphabet.
Since this number may be very large, you are required to output the answer modulo $10^9 + 7$.
