\problemname{Feed the Cactus}

Armen is worried that his cactus does not get all the nutrients it needs, so he decides to go to different towns to find the necessary items.
He lives in a country with $n$ towns, which are connected by bidirectional roads.
The road networks is such that there is exactly one route that goes between any two towns without visiting the same town twice.

Each town supplies a subset of all possible $k$ items that Armen may need.
When he visits a town, he buys all the available items that he does not yet have.
Armen wants to make one trip between two towns and make sure that he has at least $l$ out of the possible $k$ items.
Help Armen find the number of different routes he can take to find at least $l$ items.
Two routes are different, if there is a town that he visits in one but not in the other.

\hnote{AND vs OR:
This is the OR version of the problem.
You can solve it directly, or convert to the AND version using a or b = not(not a and not b).
Or you can directly do inclusion/exclusion on this, but intuitively for me it is easier to convert first (maybe because that’s the problem I have seen first)
For the AND version, the story is different: you need to collect the same coupons, so I can write the story like a lottery.}

\section*{Input}
The first line of the input contains three integers $n$ ($1 \leq n \leq 10^5$), $k$ and $L$ ($1 \leq l \leq K \leq 8$), the number of towns in the country, the number of possible items, and the number of items Armen wants to get, respectively.

The following $n$ lines contains binary strings of length $k$.
The $i$th string describes the items available in town $i$:
If there is a $1$ at position $j$ of the string, then the $j$th item is available at town $i$, otherwise it is not.

Each of the following $n - 1$ lines contain two integers $u$ and $v$, indicating that there is a road between towns $u$ and $v$.
It is guaranteed that the road network satisfies the requirements in the statement.

\section*{Output}
The output contains the number of different routes that Armen can take.

