\problemname{Messages}

Armen and Vartan like to use code words to talk to each other during the classes.
Their code words are binary strings.
Unfortunately, because of how they sit in the classroom, the teacher interrupts them when Vartan sends a message to Armen, and when Armen tries to decode the (possibly partial) message he received.
In particular, when Vartan sends a message, Armen only receives some of the first bits (maybe all).
Additionally, when Armen tries to read a code word from his cheat sheet, he only has time to read some of the first bits of it (again, maybe all).
The number of bits Armen is able to read for a given code word depends on how good the handwriting is, thus, it is always the same for each code word, but varies between different ones.

Now Armen wants to how well their system of communication works.
Thus, he has asked you to tell him, given the information he has, how many code words could match each message he receives.

\section*{Input}
The first line of the input contains two integers $n$ and $m$ ($1 \leq n, m \leq 50000$), the number of code words in Armen's and Vartan's dictionary, and the number of messages Armen receives.
The next $n$ lines of the input contain the partial code words that Armen is able to read, one per line, composed of $0$'s and $1$'s.
Each line contains at least one character.
The next $m$ lines describe the partial messages that Armen receives, in the same format as the code words.

Armen is never able to read more than $10000$ bits from each code word, and is never receives more than $10000$ bits from Vartan.
The total number of bits in the input (the sum of the lengths of the given binary strings) is at most $500000$.

\section*{Output}
The output contains $m$ lines.
The $i$th line contains one integer, the number of code words that the $i$th message could match.
